Dynein project log

### 2017-04-12 thesis/latex/thesis.tex

@@

\paragraph{Spherical domains}
Domain shape influences primarily the drag coefficients $\gamma$ of the model. These in turn affect the diffusion rate of different domains. Reducing domains to spheres adds a systematic error to the diffusion speed of each domain, which could bias step size. However, spring constants $c_b$, $c_m$ and $c_t$ also have an influence on the diffusion rate of spheres. Thus by fitting spring constants to the proper step length, the systematic error of domain size can be reduced -- ???\\

>>>>

In reality, all molecules have a degree of elasticity. A dynein model by Sarlah \textit{et. al.} models the dynein stalk as an elastic rod \cite{sarlahpaper}. However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\

@@

Domain shape influences primarily the drag coefficients $\gamma$ of the model. These in turn affect the diffusion rate of different domains. Reducing domains to spheres adds a systematic error to the diffusion speed of each domain, which could bias step size. However, spring constants $c_b$, $c_m$ and $c_t$ also have an influence on the diffusion rate of spheres. Thus by fitting spring constants to the proper step length, the systematic error of domain size can be reduced -- ???\\

Treating the conformational dynamics of the domains as harmonic energies is a simplification, but

### 2017-04-12 thesis_stuff/thesis_stuff.tex

\subsection{}

@@

>>>>

@@

\subsection{Chemical Basis of Morphogenesis}
Turing paper on how asymmetry comes about in biology\\

\subsection{Coarge-grained modeling of the structural states and transition underlying the powerstroke of dynein motor domain}
Models six AAA+ domains, CC, C-term, pre/post-powerstroke\\

Modelling the motor domain, using the post-powerstroke crystal structure, and using ``normal mode analysis'' to create a fluid transition into the pre-powerstroke state. This involves taking a crystal structure and somehow calculating the number of normal mode angle changes necessary to get it from one state to another.\\

MD is hard on molecular motors, because their kinetic timescale is fairly slow.\\

Discusses Elastic Network Model - treating atoms as springs, then finding low-frequency normal modes of the whole protein\\

Choosing just a couple modes gets lots of information
